Relationships in the extremes and their influence on competition and coexistence

### 2022-03-07 paper/Paper.Rnw
some sentences about multi-species models

We note that our expansion, like the decomposition of \cite{Ellner_2019} is generalizable to multi-species and multi-driver models. Because asymmetric tail associations exist in many ecological variables \citep{Ghosh_2020_AER}, the more specified approach of considering unique drivers of coexistence rather than E and C and the ability to consider more than two drivers, could produce interesting results?? 
More species and more drivers= more things that can be related

>>>>

%We note that our expansion, like the decomposition of \cite{Ellner_2019} is generalizable to multi-species and multi-driver models. Because asymmetric tail associations exist in many ecological variables \citep{Ghosh_2020_AER}, the more specified approach of considering unique drivers of coexistence rather than E and C and the ability to consider more than two drivers, could produce interesting results?? 
%More species and more drivers= more things that can be related
Our further decomposition and quantification of ATA contribution to coexistence can and 
should also be applied to multi-species models. 
The inclusion of multiple species introduces a multitude of relationships between species'
environmentally dependent parameters that could possibly be asymmetrically associated. 
The greater the number of species the greater the possibilities of ATAs being more important 
to their coexistence.
